Modeling vertical-axis cross-flow turbine wakes

### 2015-07-24 paper.tex
Add subsection on wake results

>>>>

\subsection{Wake characteristics}

Mean velocity profiles at one turbine diameter downstream are shown in
Figure~\ref{fig:mean-vel-profiles}. The 2-D results suffer from a blockage
mismatch, i.e. keeping the proximity of the walls constant increases the
blockage ratio.

\begin{figure}
\caption{Mean velocity profiles at $x/D=1$ from 2-D simulations, 3-D simulations
($z/H=0$), and experiments \cite{Bachant2015-JoT}.}
\label{fig:mean-vel-profiles}
\end{figure}

Turbulence kinetic energy profiles are shown in Figure~\ref{fig:k-profiles}.
Note that there are two profiles for each---one computed from the components
from the Reynolds stress tensor $R$:

\begin{equation}
k = \frac{1}{2} \left( R_{xx} + R_{yy} + R_{zz} \right);
\label{eq:k}
\end{equation}
and one that includes unsteadiness in the Reynolds-averaged velocity
\begin{equation}
k_{\mathrm{tot}} = k + \frac{1}{2} \left( 
\overline{U^\prime}^2 + 
\overline{V^\prime}^2 + 
\overline{W^\prime}^2 \right),
\label{eq:ktot}
\end{equation}
where $U^\prime = U - \overline{U}$.

\begin{figure}
\caption{Turbulence kinetic energy profiles at $x/D=1$ from 2-D simulations, 3-D
simulations ($z/H=0$), and experiments \cite{Bachant2015-JoT}.}
\label{fig:k-profiles}
\end{figure}

We see that the side of the turbine with the upwind facing blade ($+y$), despite
having regions of high turbulence intensity, is actually more dominated by
unsteadiness in the Reynolds-averaged velocity, rather than the model's
turbulence kinetic energy.
